Transforming Trash as an Artistic Act

### 2016-01-17 chapter3_final.tex
turnitin fixes
Former-commit-id: 1180ad94f12273274b95105edbcc44ca31b47297

In 20th-century, modern artists experimented with new ways of seeing and with fresh ideas about the nature of materials and functions of art. Previously paintings are based on linear perspective and realistic style. Themes are often composed of religious and mythical narratives. After the second half of the 19th-century, they started to abandon these themes and painting methods. For instance, in the works of impressionist paint brushstrokes can be easily identified. In impressionist paintings, themes are composed of everyday scenes. With Cezanne, the linear perspective is started to question and later this questioning reached to its peak point with cubism. Cubism is developed with the collaboration of Picasso and Braque. Besides, these two artists experimented non-traditional materials in their works for the first time in the scope of fine art. They continuously produced works with using different objects. They support each others art. They showed that an endless potential lay there. They collaborated with each other on the development of cubism and collage.

One of the keys to understand the importance of Cubism of Picasso and Braque, is to consider their actions and how unusual they were for the time. When Braque, and then Picasso placed industrially-produced objects into the realm of fine art they acted as artistic iconoclasts of their age.
%\todo{ref}

Collage originates from the French \textit{coller} is a technique of applying manufactured, printed, or found materials, such as pieces of newspaper, fabric, wallpaper to a panel or canvas, frequently in combination with painting. In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to construct compositions. Pasting paper is not a new technique but using this technique it in the art making is a revolutionary movement in the language of art \citep{waldman1992collage}. Collage was a major turning point in the evolution of Cubism\footnote{It needs to be noted that there is two types of Cubism; analytical and synthetic. Analytical one early phase of cubism and based on fragmentary appearance of multiple viewpoints and overlapping planes. On the other hand synthetic one is the successor phase of analytical one and formed with various textures and patterns.}, and therefore a major turning point in the whole evolution of modernist art in this century \citep{greenberg1984collage}.

Similar to the collage, assemblage is produced by the incorporation of three-dimensional objects. In 1961, the exhibition \quotes{The Art of Assemblage} was featured at the New York Museum of Modern Art. \cite{seitz1961art}, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials.

One of the earliest and notable examples of collage is Picasso’s \textit{Still Life with Chair Caning} (Figure \ref{fig:Picasso_Chair}), in which a piece of oilcloth which is used as tablecloth or self coverings with an imitation chair caning design was pasted onto the painting. This work of Picasso also can be considered as first example of assemblage because of a rope that was used to frame the picture. Picasso combined painting with already existing materials. As mentioned in the name of the work, Picasso give clues of the parts of it. For instance the oval canvas and the rope around it represent the table. Pasted chair caning signifies the chair near the table. On the table folded paper shadow represent newspaper. Further there is a cut out lemon painted onto the table. The three letters above the scrap of cloth, \quotes{JOU}, can be understood as both the beginning of the word \quotes{JOURNAL}, alluding to the customary newspaper lying across the cafe table, and as the French verb meaning \quotes{to play.} The new technique of collage allowed new possibilities of playfulness. This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas.

@@

% http://www.nybooks.com/articles/2010/12/09/artist-everything/
% http://www.artchive.com/artchive/S/schwitters.html
After Picasso and Baraque, many artists applied collage and assemblage techniques to their works. Dada artist Kurt Schwitters is one of the productive artists among them. In 1918 he created his own form of Dada in Hanover called \textit{Merz}, using rubbish elements such as labels, bus tickets and bits of broken wood in his collages and constructions. The nonsense word \textit{Merz} is generated from the name of a bank: the Kommerz und Privatbank. \textit{Merz} was soon to become a kind of brand name for almost all his productions. \cite{webster2011kurt} puts significance of Schwitters in the development of art as follows:

@@

It is claimed that the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users \citep{cerny1996recycled} Whatever their final function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.

Collages and assemblages can be composed of all types of objects such as trash and found object. The notion of found object is researched by many scholars \cite{camic2010trashed, gascoyne1935short}, but usage in the art has gained new dimensions with the Duchamp's concept of ready-made. Industrially manufactured or anything found  anymore can found a place in the art. The most famous example is \textit{Fountain} (discussed in the previous chapter), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side. Before that first one is \textit{Bicycle Wheel} (Figure \ref{fig:Duchamp_BicycleWheel}). He wrote that the idea of a bicycle wheel upside down onto a stool. Although he claimed to select objects for his ready-made without regard to beauty, he said, \quotes{To see that wheel turning was very soothing, very comforting\ldots I enjoyed looking at it, just as I enjoy looking at the flames dancing in a fireplace.} These samples were the beginning of 
shift from an art that is striving for beauty to a higher complex or hidden meaning beyond what was seen from common artifacts found in everyday living.

@@

Photobooths are machines that place crowded places and with affordable cost people can get their photos. It is a phenomena that attract attention of artist and researchers such as Martin Parr and Gerry Badger who published history of them as two volume.

In the French film Amélie\footnote{Original title: Le fabuleux destin d'Amélie Poulain, in english: The Fabulous Destiny of Amélie Poulain} directed by Jean-Pierre Jeunet in 2001, young male character collects photos that are torn up and thrown away by their owner near photo booths spread through train and metro stations of Paris. He collects them and glue them together in a photo album. In the film photo booths and found photos are centrally catalytic. Amélie falls in love with him when she realize him searching for found photos. After his photo album passed to Amélie, she looks every page of photo album again and again. Through the images of unknown people, she establishes narratives that point out the significance of these images even if they are thrown away. The important part of the film, images of a man are generated who scavenge the photos of another people. There are a lot of artist who collects discarded items but their process is not well documented. Therefore we are not aware of the artistic process.

@@

Prior to film Amélie, British artist Dick Jewell published a book in title of \quotes{Found Photos} in 1977. It is a collection of photobooth images that had been thrown away or torn up by the people in the photos. \cite{walker2010dick} comments on that it is \quotes{always a joy to look through.} Images capture diverse range of activities and expressions of people using photo booth machine. They are scavenged by the artist from the photo booths of London. The reasons of why photos are rejected vary including technical problems like flash or posing time. On the other hand, some of them are very good condition, and it is a mystery that why they are rejected. Walker explains that the

@@

Walker argues that even if photo booths are mechanic and simple application of photography while capturing everyday life, leave behind such ambiguous and mysteries that some people trace them. \quotes{Dick Jewell’s approach with Found Photos was less interventionist, presenting the images themselves in the spirit of either an anthropologist showing his finds or a conceptual artist claiming bits of the real world as ready-mades.} His mode of discovery includes climbing to look at the top of the box and looking for the nearest waste bin. Badger describes Found Photos as \quotes{both a conceptual artwork and a sociological footnote.}

@@

On the other side for another artist photographs serve a function to record his daily trash. Tim Gaudreau photographed every object that he threw away for one year. At the end around five thousand images are covered all the gallery and opened to visitors. He notes that it just started as a documentation of his discards, but later it became (part of his life and) an obsession that he can not able to easily quit off. He says that "this collection of images intimately displays what I do, what I consume. It reveals me." Like in the case of Tracey Emin trash turns to a medium that is used to express oneself. People are not only composed of the listed items in the CVs like in the film Fight Club Tyler Durden draws attention to the narrator by saying: "You are not your bank account". It is an effective way of looking things left behind rather that things put forward. Through this project, artist reached better understanding what he is and notes that this project changed his consumption choices and patterns.

@@

Filomena Cruz turns her lens to the city and its trashes that are left behind, thrown away and squeezed on the sidewalk or pavement. In her photographic series "Road Kill", she captures tiny "trash corpses" that are generally ignored and out of sight. In other words, the skin of city revealed through her photos in micro scale. On the skin of city there are lots of trash including "a piece of chewing gum with an "engraved" leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of "worthlessness" suddenly becoming meaningful" as looked through the window of they capture the city life and skin of the city that we touched. She shows us tiny details of huge cities. (Somehow these trashes for all effort succeeded to stay in the towns.) These trashes can not be removed from the city but moved ones are stacked on landfill, and they are not tiny as they are.

@@

In the documentary film, Waste Land, Vik Muniz frames portraits of \textit{catadores} who are pickers of recyclable materials on the dump. He visits them at one of the biggest open-air garbage dump outside of the Rio de Janeiro home of the millons of people. Film documents whole process of development and production of "Pictures of Garbage" made of collected trash from dump. He selects unusual materials and people for potraits rather than the powerful and notable people as commonly encountered at Renaissance. To create portraits of \textit{catadores} there is any other material than trash because of they are already build up their life in trash of city. [Also these image are sold an auction and earned money donated to the \textit{catadores}. The images of trash moved to beloved places such as homes and museums. As stated in the rubbish theory they transformed to a durable object.]

% TODO resim yanlış
\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
  \caption{Vic Muniz, \textit{Marat}, 2008, mixed media, }
  \label{fig:VicMuniz_PicturesOfGarbage}
\end{figure}

Not only monumental portraits extracted from the dump but also an orchestra is grounded up from the dump of Paraguay pioneered by Favio Chávez and Nicolás Gómez. Favio Chávez is a music teacher, and Nicolás Gómez is a garbage picker. They live in Cateura at Paraguay. It is a one of the poorest villages where people live among the sea of garbage. "A violin is worth more than a house here," says Favio Chavez in documentary film. The orchestra's director and founder. Favio Chavez director and founder of the orchestra whose instruments such as violins, flutes and cellos are built from collected trash by Nicolás Gómez. Players of the orchestra are compiled from the children who are hopeless for their future. In the midst of such an existence, these musicians have created something both special and truly awe-inspiring. They are given birth to an orchestra that plays the masterpieces of classical music composed by Mozart, Beethoven, and Vivaldi. Trash turned to treasure and totally ironic that a signifiers of high culture like classical music can be even played with imperfect instruments. For them and also, most of the people it is not affordable to buy an instrument and get the education of classical music. What they create is actually not expected from them, and their success is not limited with their location. They have given concerts around the world.

%"People realize that we shouldn't throw away trash carelessly," says Chavez at the end of the trailer. "Well, we shouldn't throw away people either." \quotes{The world send us garbage. We send back music}.

% Resistance to all hard conditions

@@

As noted that recycling as an economic strategy of survival in developing countries throughout the world. Creative production that is motivated, primarily, by adverse conditions of economic necessity. Economic survival and adaptation are influential factors for both the makers, who build an informal business on the making and selling of recycled goods and the local consumers, for whom the market for affordable, utilitarian goods is devised. (p25)

They build their musical instruments from what is available around. This project can be seen as a bricolage practice. Dictionary meaning; something constructed using whatever was available at the time. \quotes{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available. It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old. \citep{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \citep{levi1966savage}.

\quotes{\ldots someone that creates bricolage is described as a bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends.}

\begin{quote}
[He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project. His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with “whatever is at hand,” that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous constructions or destructions.\cite{levi1966savage}
\end{quote}

%\begin{quote}
%The bricoleur, says Levi-Strauss, is someone who uses 'the means at hand,' that is, the instruments he finds at his disposition around him, those which are already there, which had not been especially conceived with an eye to the operation for which they are to be used and to which one tries by trial and error to adapt them, not hesitating to change them whenever it appears necessary, or to try several of them at once, even if their form and their origin are heterogenous---and so forth. There is therefore a critique of language in the form of bricolage, and it has even been said that bricolage is critical language itself\ldots If one calls bricolage the necessity of borrowing one's concepts from the text of a heritage which is more or less coherent or ruined, it must be said that every discourse is bricoleur.\cite{derrida1993structure}
%\end{quote}

%\begin{quote}
%The engineer, whom Lévi-Strauss opposes to the bricoleur, should be the one to construct the totality of his language, syntax, and lexicon. In this sense the engineer is a myth. A subject who would supposedly be the absolute origin of his own discourse and would supposedly construct it 'out of nothing,' 'out of whole cloth,' would be the center of the verbe, the verbe itself. The notion of the engineer who had supposedly broken with all forms of bricolage is therefore a theological idea; and since Lévi-Strauss tells us elsewhere that bricolage is mythopoetic, the odds are that the engineer is a myth produced by the bricoleur.\cite{derrida1993structure}
%\end{quote}

% TODO Bunu bitirirken de bir şeyler demek gerekli.

In the scope of painting different than the works in the previous chapter (paintings on tea bags and coffee cups) historical potraits of notable people are painted onto the flattened aluminum drink cans which are disposable objects. The people in the figure X is General Jefferson C. Davis who was an officer at United States Army in 19th-century. Selected persons can be viewed as a member of the higher or ruling class of society. Therefore Kim Alsbrooks, painter of these works, might have thought that to make trash is more valuable, their face will be good. Or vice versa. She probably use trash to criticize social elite of that time.

@@

% Landy'nin yaptığı bir çok iş aslında çöple ilgili olduğu savunulabilir. Hepsinin anlatmak mümkün olmasada bir diğer için sahip olduğu tüm eşyaları bozmasıyla ilgili. Daha önceden bahsettiğim geri dönüştürme tanımları ile ilgili olarak bu işi downcycling yöntemi arasında görülebilir.

@@

Examples are not limited with these. Even if \quotes{trash is dirty and smelly trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}

% , as illustrated by the examples cited so far,

%
%
\section{The Documentary \quotes{The Gleaners and I} by Agnès Varda}
\quotes{The Gleaners and I} is a French documentary film directed by Agnès Varda in 2000. The film emphasizes diverse types of gleaning from rural to urban. According to the Merriam-Webster dictionary gleaning refers \quotes{to gather grain or other produce left by reapers}. Varda searches for the historical and current practices of gleaning in rural and urban areas of France. Historically, gleaning is the act of collecting what is left and not profitable crops after the harvest. By combining different fragments through his film, she shows that the act of gleaning also exists in various forms and styles. In particularly she curiously focuses on the (un)familiar people who glean leftover of society. Moreover, it is a self-reflexive film because the director establishes a relationship with the practice of gleaners and her film making practice. Some people glean crops; the others discarded food, and Varda gleans images.

>>>>

In 20th-century, modern artists experimented with new ways of seeing and with fresh ideas about the nature of materials and functions of art. Previously paintings are based on linear perspective and realistic style. Themes are often composed of religious and mythical narratives. After the second half of the 19th-century, they started to abandon these themes and painting methods. For instance, in the works of impressionist paint brushstrokes can be easily identified. In impressionist paintings, themes are composed of everyday scenes. With Cezanne, the linear perspective is started to question and later this questioning reached to its peak point with cubism. Cubism is developed with the collaboration of Picasso and Braque. Besides, these two artists experimented non-traditional materials in their works for the first time in the scope of fine art. They continuously produced works with using different objects. They support each others art. They showed that an endless potential lay there. They collaborated with each other on the development of cubism and collage. One of the keys to understand the significance of Cubism of Picasso and Braque, is to view their actions and how unusual they were for the time. When they placed mass produced artifacts into the realm of fine art they acted as artistic iconoclasts of their age.

Collage originates from the French \textit{coller} is a technique of pasting together manufactured, printed, or found materials, such as pieces of newspaper, fabric, wallpaper to a panel or canvas, frequently in combination with painting. In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, oil-cloth, and newspapers with oil paint on canvas to construct compositions. Pasting paper is not a new technique but using this technique it in the art making is a revolutionary movement in the language of art \citep{waldman1992collage}. \quotes{Collage was a major turning point in the evolution of Cubism\footnote{It needs to be noted that there is two types of Cubism; analytical and synthetic. Analytical one early phase of cubism and based on fragmentary appearance of multiple viewpoints and overlapping planes. On the other hand synthetic one is the successor phase of analytical one and formed with various textures and patterns.}, and therefore a major turning point in the whole evolution of modernist art in this century} \citep{greenberg1984collage}.

Similar to the collage, assemblage is produced by the incorporation of three-dimensional objects. \cite{seitz1961art}, the curator of the exhibition \quotes{The Art of Assemblage} featured at the New York Museum of Modern Art in 1961, described assemblages as being made up of preformed natural or fabricated materials, objects, or fragments not designed as art materials.

One of the earliest and notable examples of collage is Picasso’s \textit{Still Life with Chair Caning} (Figure \ref{fig:Picasso_Chair}), in which a piece of oilcloth which is used as tablecloth or self coverings with an imitation chair caning design was pasted onto the painting. This work of Picasso also can be considered as first example of assemblage because of a rope that was used to frame the picture. Picasso combined painting with already existing materials. As mentioned in the name of the work, Picasso give clues of the parts of it. For instance the oval canvas and the rope around it represent the table. Pasted chair caning signifies the chair near the table. On the table folded paper shadow represent newspaper. Further there is a cut out lemon painted onto the table. The three letters above the scrap of cloth, \quotes{JOU}, can be understood as both the beginning of the word \quotes{JOURNAL}, referring to the customary newspaper lying across the cafe table, and as the French verb meaning \quotes{to play.} The new technique of collage provided new possibilities of playfulness. This was a new way of making art; instead of painting an object or landscape, you could paste whatever it was right onto the canvas.

@@

After Picasso and Baraque, many artists applied collage and assemblage techniques to their works. Dada artist Kurt Schwitters is one of the productive artists among them. In 1918 he created his own form of Dada in Germany named \textit{Merz}, using rubbish elements such as newspapers, bus tickets and pieces of broken wood in his collages and constructions. The nonsense word \textit{Merz} is generated from the name of a bank: the Kommerz und Privatbank. \textit{Merz} was soon to become a kind of brand name for almost all his productions. \cite{webster2011kurt} puts significance of Schwitters in the development of art as follows:

@@

It is claimed that the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users \citep{cerny1996recycled} Whatever their final function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and places.

Collages and assemblages can be composed of all types of objects such as trash and found object. The notion of found object is researched by many scholars \cite{camic2010trashed, gascoyne1935short}, but usage in the art has gained new dimensions with the Duchamp's concept of ready-made. Industrially manufactured or anything found  anymore can found a place in the art. The most notable example is \textit{Fountain} (discussed in the previous chapter), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side. Before that first one is \textit{Bicycle Wheel} (Figure \ref{fig:Duchamp_BicycleWheel}). He wrote that the idea of a bicycle wheel upside down onto a stool. Although he claimed to select objects for his ready-made without regard to beauty, he said, \quotes{To see that wheel turning was very soothing, very comforting\ldots I enjoyed looking at it, just as I enjoy looking at the flames dancing in a fireplace.} These samples were the beginning of 
shift from an art that is striving for beauty to a higher complex or hidden meaning beyond what was seen from common artifacts found in everyday living.

@@

Photo booths are machines that place crowded places and with affordable cost people can get their photos. It is a phenomena that attract attention of artist and researchers such as Martin Parr and Gerry Badger who published history of them as two volume.

In the French film Amélie\footnote{Original title: Le fabuleux destin d'Amélie Poulain, in english: The Fabulous Destiny of Amélie Poulain} directed by Jean-Pierre Jeunet in 2001, young male character collects photos that are torn up and thrown away by their owner near photo booths spread through train and metro stations of Paris. He collects them and glue them together in a photo album. In the film photo booths and found photos are centrally catalytic. Amélie falls in love with him when she realize him searching for found photos. After his photo album passed to Amélie, she looks every page of photo album again and again. Through the images of unknown people, she establishes narratives that point out the significance of these images even if they are thrown away. The important part of the film, images of a man are generated who scavenge the photos of another people. There are a lot of artist who collects discarded items but their process is not well documented. Therefore we are not fully aware of their artistic process.

@@

Prior to film Amélie, British artist Dick Jewell published a book in title of \quotes{Found Photos} in 1977. It is a collection of photo booth images that had been thrown away or torn up by the people in the photos. \cite{walker2010dick} comments on that it is \quotes{always a joy to look through.} Images capture diverse range of activities and expressions of people using photo booth machine. They are scavenged by the artist from the photo booths of London. The reasons of why photos are rejected vary including technical problems like flash or posing time. On the other hand, some of them are very good condition, and it is a mystery that why they are rejected. Walker explains that the:

@@

Walker argues that even if photo booths are mechanic and simple application of photography while capturing everyday life, leave behind such ambiguous and mysteries that some people trace them. \quotes{Dick Jewell’s approach with Found Photos was less interventionist, presenting the images themselves in the spirit of either an anthropologist showing his finds or a conceptual artist claiming bits of the real world as ready-mades.} His mode of discovery includes climbing to look at the top of the photo booths and looking for the nearest waste bin. Badger describes Found Photos as \quotes{both a conceptual artwork and a sociological footnote.}

@@

On the other side for another artist photographs serve a function to record his daily trash. Tim Gaudreau photographed every object that he threw away for one year. At the end around five thousand images are covered all the gallery and opened to visitors. He notes that it just started as a documentation of his discards, but later it became (part of his life and) an obsession that he can not able to easily quit off. He says that \quotes{this collection of images intimately displays what I do, what I consume. It reveals me.} Like in the case of Tracey Emin trash turns to a medium that is used to express oneself. People are not only composed of the listed items in the CVs, economical power like pointed out in the book (and also film) Fight Club Tyler Durden draws attention to the narrator by saying: \quotes{You are not your bank account.} It is an effective way of looking things left behind rather that things put forward. Through this project, artist reached better understanding what he is and notes that this project changed his consumption choices and patterns.

@@

Filomena Cruz turns her lens to the city and its trashes that are left behind, thrown away and squeezed on the sidewalk or pavement. In her photographic series \textit{Road Kill}, she captures tiny trash corpses that are generally ignored and out of sight. In other words, the skin of city revealed through her photos in micro scale. On the skin of city there are lots of trash including \quotes{a piece of chewing gum with an engraved leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of "worthlessness" suddenly becoming meaningful} as looked through the window of they capture the city life and skin of the city that we touched. She shows us tiny details of huge cities. Somehow these trashes for all effort succeeded to stay in the towns. These trashes can not be removed from the city but moved ones are stacked on landfill, and they are not tiny as they are.

@@

In the documentary film, Waste Land, Vik Muniz frames portraits of \textit{catadores} who are pickers of recyclable materials on the dump. He visits them at one of the biggest open-air garbage dump outside of the Rio de Janeiro home of the millions of people. Film documents whole process of development and production of "Pictures of Garbage" made of collected trash from dump. He selects unusual materials and people for portraits rather than the powerful and notable people as commonly encountered at Renaissance. To create portraits of \textit{catadores} there is any other material than trash because of they are already build up their life in trash of city. Also these images are sold an auction and earned money donated to the \textit{catadores}. The images of trash moved to beloved places such as homes and museums. As stated in the rubbish theory they transformed to a durable object.

\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{graphics/vik_muniz_marat.jpg}
  \caption{Vic Muniz, \textit{Marat}, 2008, mixed media, }
  \label{fig:VicMuniz_PicturesOfGarbage}
\end{figure}

Not only monumental portraits are extracted from the dump but also an orchestra is grounded up from the dump of Paraguay pioneered by Favio Chávez and Nicolás Gómez. Favio Chávez is a music teacher, and Nicolás Gómez is a garbage picker. They live in Cateura at Paraguay. It is a one of the poorest villages where people live among the sea of garbage. \quotes{A violin is worth more than a house here,} says Favio Chávez by pointing out their hard conditions. The orchestra's director and founder. Favio Chávez director and founder of the orchestra whose instruments such as violins, flutes and cellos are built from collected trash by Nicolás Gómez. Players of the orchestra are compiled from the children who are hopeless for their future. In the middle of such an existence, these people and musicians have created something both special and truly awe-inspiring. They are given birth to an orchestra that plays the masterpieces of classical music composed by Mozart, Beethoven, and Vivaldi. Trash turned to treasure and totally ironic that a signifier of high culture like classical music can be even played with imperfect instruments. For them and also, most of the people it is not affordable to buy an instrument and get the education of classical music. What they create is actually not expected from them, and their success is not limited with their location. They have given concerts around the world and their motto is: \quotes{The world send us garbage. We send back music.}

@@

As noted that recycling is an economic strategy of survival in developing countries throughout the world \citep[25]{cerny1996recycled}. Creative production that is motivated, primarily, by adverse conditions of economic necessity. Economic survival and adaptation are influential factors for both the makers, who build an informal business on the making and selling of recycled goods and the local consumers, for whom the market for affordable, utilitarian goods is devised.

Nicolás Gómez builds musical instruments from what is available for him, in this case it is rubbish. His practice and works can be seen as an example of \textit{bricolage}. Dictionary meaning of it is something constructed by using whatever is available at hand. The French word \textit{bricoleur} is someone who works with own hands and construct \textit{bricolage}. The term coined by \cite[17]{levi1966savage} and he explains it as:

\begin{quote}
[He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project. His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with whatever is at hand, that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous construction or destruction. 
\end{quote}

In the scope of painting different than the works in the previous chapter (paintings on tea bags and coffee cups) historical portraits of notable people are painted onto the flattened aluminum drink cans which are disposable objects. The people in the figure \ref{fig:Alsbrooks} is General Jefferson C. Davis who was an officer at United States Army in 19th-century. Selected persons can be viewed as a member of the higher or ruling class of society. Therefore Kim Alsbrooks, painter of these works, might have thought that to make trash is more valuable, their face will be good or vice verse. She probably use trash to criticize social elite of that time.

@@

@@

% TODO burayı da düzeltmek gerek.
Examples are not limited with these. Even if \quotes{trash is dirty and smelly trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}

%
\section{The Documentary \quotes{The Gleaners and I} by Agnès Varda}
\quotes{The Gleaners and I} is a French documentary film directed by Agnès Varda in 2000. The film emphasizes diverse types of gleaning from rural to urban. According to the Merriam-Webster dictionary gleaning refers \quotes{to gather grain or other produce left by reapers}. Varda searches for the historical and current practices of gleaning in rural and urban areas of France. Historically, gleaning is the act of collecting what is left and not profitable crops after the harvest. By combining different fragments through his film, she shows that the act of gleaning also exists in various forms and styles. In particularly she curiously focuses on the (un)familiar people who glean leftover of society. Moreover, it is a self-reflexive film because the director establishes a relationship with the practice of gleaners and her film making practice. Some people glean crops; the others discarded food, and Varda gleans images.
